preparation OF papers for \NoCaseChange{JACoW} conferences\thanks{Work supported by ...}

### 2024-03-11 paper.tex
tables replaced by inputs

These instructions are a typical implementation of the
requirements. Manuscripts should have:
\begin{Itemize}
    \item  Either A4 (\SI{21.0}{cm}~$\times$~\SI{29.7}{cm}; \SI{8.27}{in}~$\times$~\SI{11.69}{in}) or US
           letter size (\SI{21.6}{cm}~$\times$~\SI{27.9}{cm}; \SI{8.5}{in}~$\times$~\SI{11.0}{in}) paper.
    \item  Single-spaced text in two columns of \SI{82.5}{mm} (\SI{3.25}{in}) with \SI{5.3}{mm}
           (\SI{0.2}{in}) separation. More recent versions of Microsoft Word have a default spacing of 1.5 lines;
           authors must change this to 1 line.
    \item  The text located within the margins specified in Table~\ref{l2ea4-t1}.
\end{Itemize}
\begin{table}[!hbt]
   \centering
   \caption{Margin Specifications}
   \begin{tabular}{lcc}
       \toprule
       \textbf{Margin} & \textbf{A4 Paper}                      & \textbf{US Letter Paper} \\
       \midrule
           Top         & \SI{37}{mm} (\SI{1.46}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
          Bottom       & \SI{19}{mm} (\SI{0.75}{in})            & \SI{0.75}{in} (\SI{19}{mm})        \\ %[3pt]
           Left        & \SI{20}{mm} (\SI{0.79}{in})            & \SI{0.79}{in} (\SI{20}{mm})        \\ %[3pt]
           Right       & \SI{20}{mm} (\SI{0.79}{in})            & \SI{1.02}{in} (\SI{26}{mm})        \\
       \bottomrule
   \end{tabular}
   \label{tab:margins}
\end{table}

@@

  \begin{table}[h!b]
	\setlength\tabcolsep{3.5pt}
	\centering
	\caption{Summary of Styles}
	\label{tab:styles}
	\begin{tabular}{llcc}
		\toprule
		\textbf{Style} & \textbf{Font}               & \textbf{Space}  & \textbf{Space} \\
		&                             & \textbf{Before} & \textbf{After} \\
		\midrule
		\textbf{PAPER}  & \SI{14}{pt}                 & \SI{0}{pt}      & \SI{3}{pt}  \\
		\textbf{TITLE}  & \textbf{UPPERCASE}          &                 &      \\
		& \textbf{EXCEPT FOR}         &                 &      \\
		& \textbf{REQUIRED lowercase} &                 &      \\
		& \textbf{letters}            &                 &      \\
		& \textbf{Bold}               &                 &      \\[5pt]
		%\midrule
		Author list  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{12}{pt} \\
		& UPPER- and lowercase        &                 &      \\[5pt]
		%\midrule
		\textit{Abstract} & \SI{12}{pt}                 & \SI{0}{pt}      & \SI{3}{pt} \\
		\textit{Title}  & \textit{Initial Caps}       &                 &      \\
		& \textit{Italic}             &                 &      \\[5pt]
		%\midrule
		\textbf{Section}  & \SI{12}{pt}                 & \SI{9}{pt}      & \SI{3}{pt}  \\
		\textbf{Heading}  & \textbf{UPPERCASE}          &                 &      \\
		& \textbf{bold}               &                 &      \\[5pt]
		%\midrule
		\textit{Subsection} & \SI{12}{pt}                 & \SI{6}{pt}      & \SI{3}{pt}  \\
		\textit{Heading}
                             & \textit{Initial Caps}       &                 &      \\
		& \textit{Italic}             &                 &      \\[5pt]
		%\midrule
		\textbf{Third-level} & \SI{10}{pt}                 & \SI{6}{pt}      & \SI{0}{pt}  \\
		\textbf{Heading}     
                            & \textbf{Initial Caps}       &                 &      \\
		& \textbf{Bold}               &                 &      \\[5pt]
		%\midrule
		Figure        & \SI{10}{pt}                 & \SI{3}{pt}      & $\ge$\SI{3}{pt}  \\
		Captions      &                             &                 &      \\[5pt]
		%\midrule
		Table         & \SI{10}{pt}                 & $\ge$\SI{3}{pt} & \SI{3}{pt}  \\
		Captions      &                             &                 &      \\[5pt]
		%\midrule
		Equations     & \SI{10}{pt} base font       & $\ge$\SI{6}{pt}     & $\ge$\SI{6}{pt} \\[5pt]
		%\midrule
		References      & \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt} \\
        when $\le9$ 	& \verb|\bibliography{9}|	&                 &  \\[5pt]
        Refs. $\ge10$ 	& \SI{9}{pt}				& \SI{0}{pt}      & \SI{3}{pt}  \\
                		& \verb|\bibliography{99}|	&    &    \\
		\bottomrule   %\SI{0.25}{in}
	\end{tabular}
\end{table}

>>>>

These instructions are a typical implementation of the
requirements. Manuscripts should have:
\begin{Itemize}
    \item  Either A4 (\SI{21.0}{cm}~$\times$~\SI{29.7}{cm}; \SI{8.27}{in}~$\times$~\SI{11.69}{in}) or US
           letter size (\SI{21.6}{cm}~$\times$~\SI{27.9}{cm}; \SI{8.5}{in}~$\times$~\SI{11.0}{in}) paper.
    \item  Single-spaced text in two columns of \SI{82.5}{mm} (\SI{3.25}{in}) with \SI{5.3}{mm}
           (\SI{0.2}{in}) separation. More recent versions of Microsoft Word have a default spacing of 1.5 lines;
           authors must change this to 1 line.
    \item  The text located within the margins specified in Table~\ref{l2ea4-t1}.
\end{Itemize}

\input{tables/margins.tex}

@@

\input{tables/styles.tex}
